\documentclass[12pt, letterpaper]{article}
\usepackage{SyllabusStyle}
\setlength{\parindent}{0pt}
\geometry{margin=1.1in}

\begin{document}
\begin{center}
	{\Large \textsc{Principles of Chemistry II} (CHEM 1225) Honors Assignment}
\end{center}

To receive honors credit in this course, students must complete the assignment detailed below. This assignment takes the place of a normal honors contract.

\section*{Intention:}
The SUU Honors Program intends to foster the following student learning outcomes:
\begin{itemize}
  \item The ability to understand complex issues from diverse perspectives
  \item The ability to understand how scholars in different disciplines observe and interpret the world
  \item The development of skills in self-expression, critical thinking, information gathering, and problem-solving
  \item To write analytical or scientific papers of substantial length and depth
\end{itemize}
\section*{Assignment:}
\begin{enumerate}
  \item Attend the \nth{12} Annual SUU Festival of Excellence

    \href{https://www.suu.edu/excellence/program}{https://www.suu.edu/excellence/program}
    \begin{description}
      \item[When: ] Tuesday, March 26, 2024
      \item[Where: ] Various rooms on SUU campus (see the program linked above)
    \end{description}
  \item Observe poster presentations and/or oral presentations related to your interests
  \item Choose a single research project to focus on for this assignment
  \item Interview the faculty mentor and/or students who conducted the research project
  \item Create a 2-3 page essay.

    Essay Instructions:
    \begin{itemize}
      \item The essay will by typed using 12 point font, full justification, and double-spaced with 1-inch margins. A cover sheet is \emph{not} necessary. Your name, this course number, and the date will appear in the top-right corner of the first page of the essay as follows:

        \hspace{0.8\linewidth} 
        \begin{minipage}[r]{0.2\linewidth}
          ~
          
            Your name

            CHEM 1220-01

            April 17, 2024  
          
        \end{minipage}
      \item Topics to inlude:
        \begin{itemize}
          \item The title of the research project that you chose to write about
          \item The people who conducted the research project that you chose to write about
          \item The closest field of science or engineering related to this research project
        \end{itemize}
      \item Topics to consider:
        \begin{itemize}
          \item Why are you interested in this research project?
          \item What is the importance of the research project?
          \item How was the research project carried out?
          \item What equipment and materials were necessary to carry out the research project?
          \item How could you get involved with a similar research project?
          \item What are the benefits to students who get involved with a research project?
          \item What have you learned from completing this assigment?
        \end{itemize}
    \end{itemize}
  \item Due Wednesday, April 17, 2024
\end{enumerate}
\section*{Evaluation:}
The essay will be evaluated based on clarity, thoroughness, and alignment with the instructions listed above. In addition, the essay will be evaluated on the students' ability to correlate the assignment with the intentional learning outcomes of the Honors Program. 
\end{document}
